Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-04-07 chap.tex
CSA section [WIP]

Introduced in \citet{Xavier-De-Souza2010}, \emph{Coupled Simulated Annealing} (CSA) is a generalisation of \emph{Simulated Annealing} (SA).

CSA follows the same procedure as \emph{grid search}, but after evaluation of the objective $Q(.)$ on the grid, each grid point is iteratively mutated in a random walk fashion. This mutation is accepted or rejected according to the new value of $Q(.)$ as well as its value on the other grid points. This procedure is iterated until some stop criterion is reached.

>>>>

Introduced in \citet{Xavier-De-Souza2010}, \emph{Coupled Simulated Annealing} (CSA) is a family of optimization techniques which is a generalization of \emph{Simulated Annealing} (SA) \citep{Kirkpatrick671}. The CSA optimization technique can be understood as a set of parallel SA processes which are coupled by their acceptance probabilities.

From an implementation point of view, CSA follows the same procedure as \emph{grid search}, but after evaluation of the objective $Q(.)$ on the grid, each grid point is iteratively mutated in a random walk fashion. This mutation is accepted or rejected according to the new value of $Q(.)$ as well as its value on the other grid points. This procedure is iterated until some stop criterion is reached.
